---
title: "10_SALG-histograms"
author: "Deidre Jaeger"
date: "4/2/2020"
output: pdf_document
---

```{r global_options, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, results= FALSE, echo= TRUE)

# echo = false to turn off code

```


```{r load-libraries, echo = FALSE}
library(ggplot2)
library(dplyr)
library(tidyr) #for pivot
library(lubridate) # for dates
library(agricolae) # for the tukey test
```


```{r load-data, echo = FALSE}

# pre <- read.csv(file = "data/student-data/Pre-assessment EBIO 1250- section 012_March 5, 2020_10.19.csv",
#                 header = T,
#                 stringsAsFactors = F)
# 
# post <- read.csv(file = "data/student-data/post-assessment EBIO 1250- section 012_March 5, 2020_10.19.csv",
#                  header = T,
#                  stringsAsFactors = F)

pre <- read.csv(file = "data/student-data/Pre-assessment2 EBIO 1250- section 012_March 5, 2020_17.33.csv",
                header = T,
                stringsAsFactors = F,
                na.strings=c("","NA"))

post <- read.csv(file = "data/student-data/post-assessment2 EBIO 1250- section 012_March 5, 2020_17.33.csv",
                 header = T,
                 stringsAsFactors = F,
                 na.strings=c("","NA"))


```

```{r clean-fuse-datasets, echo = FALSE}
# add a type column
pre$type <- "pre2019"
post$type <- "post2019"

# remove the first 2 rows in each dataset that dont contain variables
pre <- pre[-c(1:2),]
post <- post[-c(1:2),]


colnames(post) == colnames(pre)


# poking around
ncol(post)
which(colnames(post)=="Q24" )
which(colnames(post)=="Q25" )
colnames(pre[61])

# remove consent questions
post2 <- post[, -c(which(colnames(post)=="Q24" ), which(colnames(post)=="Q25" ))]

# remove weird parent topics questions
pre2 <- pre[, -c(which(colnames(pre)== colnames(pre[61])),which(colnames(pre)==colnames(pre[62]) ))]

# check that column names the same
colnames(post2) == colnames(pre2)

# Fuse the datasets
pre.post <- rbind(pre2, post2)


# clean up classes being coded as characters
str(pre.post)

# change columns of quantitative questions to numeric
pre.post[, (which(colnames(pre.post)=="Q8.Q13_1" ):which(colnames(pre.post)=="Q34.40_7"))] <- sapply(pre.post[, (which(colnames(pre.post)=="Q8.Q13_1" ):which(colnames(pre.post)=="Q34.40_7"))], as.numeric)

# Check structure
str(pre.post)

# change factor order
pre.post$type <- factor(pre.post$type, levels = c("pre2019","post2019"))

str(pre.post$type)

```


The SALG questions are not the same pre/post, so need to just look at histograms and compare before/after

Non-content questions
(SALG) Presently I Can…
Scale Response Category 1 = I gained nothing/not at all 2 = I gained a little 3 = I gained somewhat 4 = I gained a lot 5 = I gained a great deal [different scale than Pre-Assessment]
Q20. Find articles relevant to a particular problem in professional journals or elsewhere
Q21. Critically read articles about issues raised in class
Q22. Identify patterns in data
Q23. Recognize a sound argument and appropriate use of evidence
Q24. Develop a logical argument
Q25. Write documents in discipline-appropriate style and format
Q26. Work effectively with others
Q27. Prepare and give oral presentations

```{r SALG-presently-Ican, results= TRUE}

# Q20. Find articles relevant to a particular problem in professional journals or elsewhere
# improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_1, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q21. Critically read articles about issues raised in class
# some improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_2, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q22. Identify patterns in data
# improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_3, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q23. Recognize a sound argument and appropriate use of evidence
# improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_4, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q24. Develop a logical argument
# improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_5, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q25. Write documents in discipline-appropriate style and format
# improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_6, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q26. Work effectively with others
# minor improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_7, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q27. Prepare and give oral presentations
# improvement
ggplot(data = pre.post, mapping = aes(x=Q20.27_8, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

```


(SALG) Presently I Understand…
Scale Response Category 1 = I gained nothing/not at all 2 = I gained a little 3 = I gained somewhat 4 = I gained a lot 5 = I gained a great deal [different scale than Pre-Assessment]
Q28. How ideas we will explore in this class relate to ideas I have encountered in other classes within this subject area
Q29. How ideas we will explore in this class relate to ideas I have encountered in classes outside of this subject area
Q30. How studying this subject helps people address real world issues


```{r SALG-i-understand, results = TRUE}
# Q28. How ideas we will explore in this class relate to ideas I have encountered in other classes within this subject area
# no/minor improvment
ggplot(data = pre.post, mapping = aes(x=Q28.30_1, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q29. How ideas we will explore in this class relate to ideas I have encountered in classes outside of this subject area
# less consensus
ggplot(data = pre.post, mapping = aes(x=Q28.30_2, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

# Q30. How studying this subject helps people address real world issues
# improvement
ggplot(data = pre.post, mapping = aes(x=Q28.30_3, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

```


(SALG) Presently I Am…
Scale Response Category 1 = I gained nothing/not at all 2 = I gained a little 3 = I gained somewhat 4 = I gained a lot 5 = I gained a great deal [different scale than Pre-Assessment]
Q31. Enthusiastic about this subject
Q32.  Interested in discussing this subject area with friends or family
Q33. Interested in taking or planning to take additional classes in this subject


```{r SALG-I-am, results = TRUE}

# Q31. Enthusiastic about this subject
# overall gained
ggplot(data = pre.post, mapping = aes(x=Q31.33_1, color = type)) +
  geom_histogram() +
  facet_wrap(~type)


# Q32.  Interested in discussing this subject area with friends or family
# imrproved
ggplot(data = pre.post, mapping = aes(x=Q31.33_2, color = type)) +
  geom_histogram() +
  facet_wrap(~type)


# Q33. Interested in taking or planning to take additional classes in this subject
# overall gains
ggplot(data = pre.post, mapping = aes(x=Q31.33_3, color = type)) +
  geom_histogram() +
  facet_wrap(~type)

```
